Level-Set method on \texttt{p4est}

### 2014-12-05 paper/tex/scaling_results.tex
Finished the scaling results. Now we need to add in Stefan application

\begin{table}[htbp]
	\centering
	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{|c|c|cccc|cccc|}
	\hline
	\multirow{2}{*}{CFL} & \multirow{2}{*}{Metric} & \multicolumn{4}{|c|}{First Iteration} & \multicolumn{4}{|c|}{Last Iteration} \\
	\cline{3-10}
											 & 												 & min & max & avg & stddev 					   & min & max & avg & stddev 						\\
	\hline
	\multirow{3}{*}{1}   & $N_p$        & 6.67E+04 & 1.59E+05 & 7.57E+04 & 4.86E+03 & 6.69E+04 & 1.55E+05 & 7.57E+04 & 4.73E+03 \\
										   & $N_m$ 			  & 18 			 & 387 		  & 47.55 	 & 31.72 		& 18 			 & 392 			& 47.55 	 & 31.19 		\\
										   & $V_m$ (MB)   & 4.01E-01 & 2.93E+00 & 7.25E-01 & 1.95E-01 & 4.13E-01 & 3.91E+00 & 9.68E-01 & 2.62E-01 \\
										   & $T_\max$ (s) & \multicolumn{4}{|c|}{6.96E-01}						& \multicolumn{4}{|c|}{3.67E-01}						\\
	\hline
	\multirow{3}{*}{10}  & $N_p$        & 5.56E+04 & 1.63E+05 & 7.57E+04 & 6.07E+03 & 6.65E+04 & 1.33E+05 & 7.57E+04 & 4.50E+03 \\
										   & $N_m$ 			  & 17 			 & 387 		  & 46.73 	 & 31.78 		& 19 			 & 393 			& 46.68 	 & 27.93 		\\
										   & $V_m$ (MB)   & 4.01E-01 & 3.06E+00 & 8.40E-01 & 2.21E-01 & 4.40E-01 & 4.80E+00 & 2.14E+00 & 9.88E-01 \\
											 & $T_\max$ (s) & \multicolumn{4}{|c|}{7.55E-01}						& \multicolumn{4}{|c|}{3.30E-01}						\\
	\hline
	\multirow{3}{*}{100} & $N_p$        & 8.28E+02 & 4.98E+05 & 7.57E+04 & 3.14E+04 & 6.30E+04 & 1.10E+05 & 7.57E+04 & 4.20E+03 \\
										   & $N_m$ 			  & 11 			 & 373 		  & 41.18 	 & 30.85 		& 16 			 & 357 			& 41.77 	 & 22.66 		\\
										   & $V_m$ (MB)   & 5.28E-01 & 1.01E+01 & 2.65E+00 & 9.24E-01 & 9.76E-01 & 4.86E+00 & 3.78E+00 & 5.69E-01 \\
											 & $T_\max$ (s) & \multicolumn{4}{|c|}{9.25E-01}						& \multicolumn{4}{|c|}{3.55E-01}						\\
	\hline
	\end{tabular}
	}
	\caption{Detailed load balancing and communication information for the advection test problem for $\text{CFL} = 1$, $\text{CFL} = 10$, and $\text{CFL} = 100$. Note how increasing the CFL number causes load imbalance and increases the communication volume while it does not affect the number of sent and received messages during an iteration of Semi-Lagrangian step.}
	\label{tab:communication}
\end{table}

@@

Finally we present scaling results of our parallel reinitialization algorithm where we extensively make use of algorithm \ref{alg:overlap} for overlapping computation with communication when computing spatial derivatives. Our test is consisted of computing the signed distance to a collection of 100 sphere, whose radii and centers have been selected randomly (c.f. \ref{fig:reinit}). Computation is conducted on a forest with a $3\times3\times3$ macromesh and level-10 octree per macro-cell which results in a final grid with roughly $350$M nodes.
\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{figures/reinit.png}
\label{fig:reinit}
\caption{Computational domain for the reinitialization test}
\end{figure}

>>>>

\begin{table}[htbp]
	\centering
	\resizebox{\columnwidth}{!}{
	\begin{tabular}{|c|c|cccc|cccc|}
	\hline
	\multirow{2}{*}{CFL} & \multirow{2}{*}{Metric} & \multicolumn{4}{|c|}{First Iteration} & \multicolumn{4}{|c|}{Last Iteration} \\
	\cline{3-10}
											 & 												 & min & max & avg & stddev 					   & min & max & avg & stddev 						\\
	\hline
	\multirow{3}{*}{1}   & $N_p$        & 6.67E+04 & 1.59E+05 & 7.57E+04 & 4.86E+03 & 6.69E+04 & 1.55E+05 & 7.57E+04 & 4.73E+03 \\
										   & $N_m$ 			  & 18 			 & 387 		  & 47.55 	 & 31.72 		& 18 			 & 392 			& 47.55 	 & 31.19 		\\
										   & $V_m$ (MB)   & 4.01E-01 & 2.93E+00 & 7.25E-01 & 1.95E-01 & 4.13E-01 & 3.91E+00 & 9.68E-01 & 2.62E-01 \\
										   & $T_\max$ (s) & \multicolumn{4}{|c|}{6.96E-01}						& \multicolumn{4}{|c|}{3.67E-01}						\\
	\hline
	\multirow{3}{*}{10}  & $N_p$        & 5.56E+04 & 1.63E+05 & 7.57E+04 & 6.07E+03 & 6.65E+04 & 1.33E+05 & 7.57E+04 & 4.50E+03 \\
										   & $N_m$ 			  & 17 			 & 387 		  & 46.73 	 & 31.78 		& 19 			 & 393 			& 46.68 	 & 27.93 		\\
										   & $V_m$ (MB)   & 4.01E-01 & 3.06E+00 & 8.40E-01 & 2.21E-01 & 4.40E-01 & 4.80E+00 & 2.14E+00 & 9.88E-01 \\
											 & $T_\max$ (s) & \multicolumn{4}{|c|}{7.55E-01}						& \multicolumn{4}{|c|}{3.30E-01}						\\
	\hline
	\multirow{3}{*}{100} & $N_p$        & 8.28E+02 & 4.98E+05 & 7.57E+04 & 3.14E+04 & 6.30E+04 & 1.10E+05 & 7.57E+04 & 4.20E+03 \\
										   & $N_m$ 			  & 11 			 & 373 		  & 41.18 	 & 30.85 		& 16 			 & 357 			& 41.77 	 & 22.66 		\\
										   & $V_m$ (MB)   & 5.28E-01 & 1.01E+01 & 2.65E+00 & 9.24E-01 & 9.76E-01 & 4.86E+00 & 3.78E+00 & 5.69E-01 \\
											 & $T_\max$ (s) & \multicolumn{4}{|c|}{9.25E-01}						& \multicolumn{4}{|c|}{3.55E-01}						\\
	\hline
	\end{tabular}
	}
	\caption{Detailed load balancing and communication information for the advection test problem for $\text{CFL} = 1$, $\text{CFL} = 10$, and $\text{CFL} = 100$. Note how increasing the CFL number causes load imbalance and increases the communication volume while it does not affect the number of sent and received messages during an iteration of Semi-Lagrangian step.}
	\label{tab:communication}
\end{table}

@@

Finally we present scaling results of our parallel reinitialization algorithm where we extensively make use of algorithm \ref{alg:overlap} for overlapping computation with communication when computing spatial derivatives. Our test is consisted of computing the signed distance to a collection of 100 sphere, whose radii and centers have been chosen randomly. Test is perform on a small, level-8 octree with nearly 21M and a larger, level-10 octree with nearly 337M grid points. In both cases the forest is built on a $3\times3\times3$ macro-mesh. Figures \ref{fig:reinit} illustrates that our reinitialization algorithm and, in particular the overlapping strategy presented in algorithm \ref{alg:overlap}, scales very well. In general we expect similar scaling results for any local, finite-difference based calculations on octrees that can efficiently utilize algorithm \ref{alg:overlap}. 
\begin{figure}
\centering
\subfigure[]{\includegraphics[width=0.45\textwidth]{figures/Reinit_Small.pdf}}
\subfigure[]{\includegraphics[width=0.45\textwidth]{figures/Reinit_Large.pdf}}
\caption{Scalability of the reinitialization test for a small (left) and large octrees with roughtly 21M and 337M grid points, respectively. Excellent results are obtained in both cases, illustrating the scalability of the overlapping strategy (c.f. algorithm \ref{alg:overlap}).}
\label{fig:reinit}
\end{figure}
